Dissertation reading notes

### 2023-07-16 Texfiles/Draft1.tex
Lots of lifecycle work

Standard economic theory suggests that retirement annuities should be highly prized by individuals as a way to
insure against the risk of late death \cite{yaari_65}. However, in developed countries rates of annuitization are far below the
levels that theory predicts. In this paper I test two competing hypotheses for the annuity problem: bequests and
pessimistic life expectancy. Under the coalition government in the UK the law regarding the use of private defined
contribution pensions changed. Individuals were no longer forced to annuitise their pension pots and could access
them in a variety of ways such as lump sum withdrawals or income drawdown and subsequently the number of annuities
sold in the UK dropped precipitously.

@@

                  \item Need annuity theory references -- Yarri?
            \end{enumerate}
      \item Lit review
      \item Models
      \item Empirical
            \begin{enumerate}
                  \item Diff in diff
                  \item RDD
                  \item Matching?
                  \item can I use anything I learnt in panel?
                        In some sense the decision to annuitise is a discrete choice problem so I could use something from there.
            \end{enumerate}
      \item Conclusion
\end{itemize}

>>>>

Standard economic theory suggests that retirement annuities should be highly prized by individuals as a way to
insure against the risk of late death \cite{yaari_65}. However, in developed countries rates of annuitization are far below the
levels that theory predicts. In this paper I test two competing hypotheses for the annuity problem: bequests and
pessimistic life expectancy. In most developed countries, individuals are forced to contribute to either a defined 
benefit or defined contribution pension. A defined benefit pension accumulates throughout your job tenure as  
 Under the coalition government in the UK the law regarding the use of private defined
contribution pensions changed. Individuals were no longer forced to annuitise their pension pots and could access
them in a variety of ways such as lump sum withdrawals or income drawdown and subsequently the number of annuities
sold in the UK dropped precipitously.

@@

                  \item Add bit about DC/DB pensions in the intro. Also talk about heterogeneity across countries.
                        Some countries want to move towards more annuitisation. This annual review is a good source of info
                        \cite{banks_crawford_ar_2022}
            \end{enumerate}
      \item Lit review
      \item Models
      \item Empirical
            \begin{enumerate}
                  \item Diff in diff
                  \item RDD
                  \item Matching?
                  \item can I use anything I learnt in panel?
                        In some sense the decision to annuitise is a discrete choice problem so I could use something from there.
            \end{enumerate}
      \item Conclusion
\end{itemize}

### 2023-07-16 Texfiles/Notes.tex
Lots of lifecycle work

@@

                    \item Do I want to add defined pension income to the model? Yes I think so. 
          \end{enumerate}
\end{itemize}

>>>>

\subsection{\textbf{14-07}}
\begin{itemize}
      \item Pension wealth variables from IFS -- I could illustrate
            the method with just financial wealth and then use pension wealth calculations
            as well. Pension wealth gives us retirement income. This leaves financial wealth to be
            invested in annuities.

      \item Apparently there are pension wealth variables for DC pensions?
            Cant find in harmonized but perhaps they are in the pension files?

      \item Could subjective survival probs also explain slow asset decumulation. And then by the time they are old
            they have medical risks.

      \item "Allowing individuals to solve optimisation problems using hueristics"
\end{itemize}

@@

                  \item Do I want to add defined pension income to the model? Yes I think so.
                  \item Can also check the consumption responses of individuals who think they are going to leave a bequest.
            \end{enumerate}
\end{itemize}
